Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2018-01-10 CCIAQVTS/CCIAQVTS.tex
cover letter first draft complete

    \section{Introduction}
    \label{sec:introduction}
    In recent decades, the technical utility of quantum mechanics has become abundantly clear. In the realm of computation, quantum algorithms --- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} --- scale exponentially better than their classical counterparts. In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} --- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill. Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}. Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.

>>>>

    \section{Introduction}
    \label{sec:introduction}
    In recent decades, the technical utility of quantum mechanics has become abundantly clear. In the realm of computation, quantum algorithms --- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} --- scale exponentially better than their classical counterparts. In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} --- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill. Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}. Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and to certify that the quantum advantage is genuine.
